---
title: "tabdif Vignette"
author: "[David Montaner](http://www.dmontaner.com)"
created: 2017-02-27
modified: 2017-02-27
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tabdif Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, results = "hide"}
options (width = 80)
library (datasets)
```


About
--------------------------------------------------------------------------------


Example Data
--------------------------------------------------------------------------------

Imagine we have two simmilar data.frames `iris0` and `iris1`

```{r}
iris0 <- iris1 <- cbind (iris, N = 1:50)
```

with some some cell differences

```{r}
iris1[4, 1] <- 80
iris1[5, 2] <- 90
iris1[6, 3:4] <- 100 
```

with some different rows

```{r}
iris0 <- iris0[-(1:3),]
iris1 <- iris1[-150]
```

wth some different columns

```{r}
iris0[,"mycol0"] <- "A"
iris1[,c ("mycol1", "mycol2")] <- "B"
```

Imagine some of the rows are duplicated 
(or better that they have dulicated id)


```{r}
iris0 <- rbind (iris0, iris0[10,])
iris1 <- rbind (iris1, iris1[20:21,])
head (iris0)
head (iris1)
```



Usage
--------------------------------------------------------------------------------

Then we can use the function `compareDataFrames` 
in the `tabdif` package to spot differences across the two tables.


`compareDataFrames` cretes a list of classs `dfcomp` wth the following information:

Number of Deleted Columns: 0
 
Number of New Columns: 0
 
Number of Changed Column Classes: 0
 
Number of Duplicated Rows Old Table: 0
 
Number of Duplicated Rows New Table: 0
 
Number of Deleted Rows: 0
 
Number of New Rows: 0
 
Number of Changed Cells: 0


- "del.cols"      "new.cols"      "dif.col.class" "dup.rows.old" 
[5] "dup.rows.new"  "del.rows"      "new.rows"      "dif.cells"    





```{r}
library (tabdif)

dif <- compareDataFrames (iris0, iris1, rowKeys = c ("N", "Species"))

summary (dif)

dfcomp2xlsx (dif, file = "dif_report.xlsx")

dif
```



```{r, echo = FALSE, results = "hide"}
unlink ("dif_report.xlsx")
```
