---
title: "tabdif Vignette"
author: "[David Montaner](http://www.dmontaner.com)"
created: 2017-02-27
modified: 2017-02-27
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tabdif Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, results = "hide"}
options (width = 80)
library (datasets)
```


About
--------------------------------------------------------------------------------


Example Data
--------------------------------------------------------------------------------

Imagine we have two similar data.frames `iris0` and `iris1`

```{r}
iris0 <- iris1 <- cbind (iris, N = 1:50)
```

with some some cell differences

```{r}
iris1[4, 1] <- 80
iris1[5, 2] <- 90
iris1[6, 3:4] <- 100 
```

with some different rows

```{r}
iris0 <- iris0[-(1:3),]
iris1 <- iris1[-150]
```

with some different columns

```{r}
iris0[,"mycol0"] <- "A"
iris1[,c ("mycol1", "mycol2")] <- "B"
```

Imagine some of the rows are duplicated 
(or better that they have duplicated id)


```{r}
iris0 <- rbind (iris0, iris0[10,])
iris1 <- rbind (iris1, iris1[20:21,])
head (iris0)
head (iris1)
```


Usage
--------------------------------------------------------------------------------

Then we can use the function `compareDataFrames` 
in the `tabdif` package to spot differences between the two tables.

`compareDataFrames` creates a list of class `dfcomp` with the following information:

- Deleted Columns: Column names in the first (_old_) data.frame not found in the second one (_new_).
- New Columns:     Column names in the second        data.frame not found in the first  one.
- Changed Column Classes: Columns with different class in the first and second data.frames.
- Duplicated Rows Old Table: Rows with duplicated ids in the first  data.frame. This rows are not compared.
- Duplicated Rows New Table: Rows with duplicated ids in the second data.frame. This rows are not compared.
- Deleted Rows: Rows in the first  data.frame which ID is not found in the second data.frame.
- New Rows:     Rows in the second data.frame which ID is not found in the first  data.frame.
- Changed Cells: Cells which have changed from one dataset to the other.


```{r}
library (tabdif)
dif <- compareDataFrames (iris0, iris1, rowKeys = c ("N", "Species"))
summary (dif)
```


The `dfcomp` object can easily be exported to an _xlsx_ file. 
Each element of the list above mentioned will be in a tab of the _xlsx_ file. 

```{r}
dfcomp2xlsx (dif, file = "dif_report.xlsx")
```

```{r, echo = FALSE, results = "hide"}
unlink ("dif_report.xlsx")
```
